There once was a grid at ol' Carkeek

### 2016-03-04 Manuscript/carkeek_grid.tex
added trace plots
add to introduction

%---------------------------------INTRODUCTION----------------------------------
\section*{Introduction}
For centuries, humankind has wondered: If I have two apples, and someone gives me another two apples, how many apples do I have? Some people did this \citep{Darwin1859}.

@@

%--------------------------------CONTRIBUTIONS----------------------------------
\section*{Author Contributions}
Conceived and designed the experiments: James L. O'Donnell, Ryan P. Kelly, A. Ole Shelton.
Collected the data: James L. O'Donnell, Greg Williams, Natalie C. Lowell, Ryan P. Kelly, A. Ole Shelton, .
Conducted the analyses: .
Wrote the first draft: .
Edited the manuscript: .

>>>>

%---------------------------------INTRODUCTION----------------------------------
\section*{Introduction}

Biodiversity surveillance is being revolutionized by DNA-based detection of organisms from environmental samples. ?(specifically speed and scope of ecological studies).
Many researchers are justifiably cautious about the ?(adoption) of this new form of data.
Their apprehension is rooted in the premise that traditional survey approaches are more accurate because the chain of inference between observation and ecological data is usually short: A researcher sees two swans in Lake Hopatcong and infers the lake is occupied by at least 2 swans.
DNA based surveys, on the other hand, consist of a longer chain of inference ?(including several links at which the links are complex or unknown)?:
Dna sequences are observed from a sequencer, the sequencer sequences products of a polymerase chain reaction (PCR), PCR amplified sequences from a purified DNA sample, DNA is purified (extracted) from an environmental sample, environmental samples contain DNA from organisms present, the organisms present are representative of the biological community about which we wish to make inference. (Could tie this to the swans of Lake Hopatcong).
Clearly, this process is more complex than visual surveys. ?(and includes several steps at which the relationship between stages is complex or unknown)

@@

%--------------------------------CONTRIBUTIONS----------------------------------
\section*{Author Contributions}
Conceived and designed the experiments: James L. O'Donnell, Ryan P. Kelly, A. Ole Shelton.
Collected the data: James L. O'Donnell, Greg Williams, Natalie C. Lowell, Ryan P. Kelly, A. Ole Shelton, Jameal F. Samhouri.
Conducted the analyses: .
Wrote the first draft: .
Edited the manuscript: .
